Inefficient Concessions and Mediation

### 2021-02-13 notes.tex
rename mathematica file

We compare them to find when the welfare under the mediator is larger:
	\begin{multline*}
		\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
		\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
	\end{multline*}							
Eliminating common terms:
	\begin{equation*}
		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
	\end{equation*}	
Rearranging:
	\begin{equation*}
		\frac{1}{1-\de_h}\left\{pTe - 1 \right\} \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
	\end{equation*}

Rearranging:
\begin{equation*}
		\frac{pTeg_M}{1-\de_h} \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} - p(T+D)
	\end{equation*}	
This is what I implement in Mathematica Notebook ``We greater than W0.nb''
\begin{itemize}
	\item So far, I've been able to find an instance that satisfies this equation: e = 11/64, $\de_h = 15/16$, $\de_l = 0.5$, $p = 0.5$, T = 1, W = 1, D = 1
	\item This is ``Parameterization 6'' above and in R file ``e-g calculations.R''
\end{itemize}

>>>>

Ultimately I gave up on this because Mathematica couldn't solve the expressions with welfare under the mediator -- I believe this is because of the asymptote.
\begin{itemize}
	\item Instead, I looked for a sufficient condition to make welfare increase to the left of the asymptote (i.e. when the gift is positive).
\end{itemize}
